Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-05-05 research_proposal/research_proposal_draft.qmd
expand on OLS and WLS

The choice of $\boldsymbol{G}$ determines the composition of reconciled forecasts $\tilde{\boldsymbol{y}}_h$. Methods are developed to estimate $\boldsymbol{G}$, including the OLS and WLS, proposed by @Hyndman2011-jv and @Hyndman2016-ic respectively.

- expand on about OLS and WLS

@@

@Wickramasuriya2019-xq also showed that MinT is an algebraical generalisation of the GLS, and the OLS and WLS methods are special cases of MinT when $\boldsymbol{W}_h$ is a diagonal or identity matrix, respectively. However, the MinT solution hinges on a reliable estimate of $\boldsymbol{W}_h$, which is challenging to estimate in high-dimensional setting. Therefore, we will be exploring alternative covariance estimators.

>>>>

\color{red}

The choice of $\boldsymbol{G}$ determines the composition of reconciled forecasts $\tilde{\boldsymbol{y}}_h$. Methods are developed to estimate $\boldsymbol{G}$, the first attempts at least squares forecast reconciliation were made by @Hyndman2011-jv.

The proposed the optimal $\boldsymbol{G}$ based on the regression model:

$$
\hat{\boldsymbol{y}}_h = \boldsymbol{S} \boldsymbol{\beta}_h + \boldsymbol{\epsilon}_h,
$$

where $\boldsymbol{\epsilon}_h = \tilde{\boldsymbol{y}}_h - \hat{\boldsymbol{y}}_h$ is the coherency error with variance $\boldsymbol{V}_h$. This led to the GLS solution: $\boldsymbol{G} = (\boldsymbol{S}' \boldsymbol{V}_h^{-1} \boldsymbol{S})^{-1} \boldsymbol{S}' \boldsymbol{V}_h^{-1}$

However, the covariance matrix $\boldsymbol{V}_h$ is unknown (and later shown by @Wickramasuriya2019-xq to be unidentifiable), and replaced by an identity matrix. The method then collapses into an OLS solution: $\boldsymbol{G} = (\boldsymbol{S}' \boldsymbol{S})^{-1} \boldsymbol{S}'$.

An obvious drawback of the OLS solution is that it weights all series in any level equally. The issue prompted @Hyndman2016-ic to propose a WLS solution, where the series are weighted by the inverse variances of the base forecasts. The WLS solution is $\boldsymbol{G} = (\boldsymbol{S}' \boldsymbol{\Lambda}_h^{-1} \boldsymbol{S})^{-1} \boldsymbol{S}' \boldsymbol{\Lambda}_h^{-1}$. $\boldsymbol{\Lambda}_h = \text{diag} (\boldsymbol{W}_h)$ and $\boldsymbol{W}_h = Var(\boldsymbol{y}_h - \hat{\boldsymbol{y}}_h)$.

\color{black}

@@

@Wickramasuriya2019-xq also showed that MinT is an algebraical generalisation of the GLS, and the OLS and WLS methods are special cases of MinT when $\boldsymbol{W}_h$ is an identity and a diagonal matrix, respectively. However, the MinT solution hinges on a reliable estimate of $\boldsymbol{W}_h$, which is challenging to estimate in high-dimensional setting. Therefore, we will be exploring alternative covariance estimators.
